Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2021-04-18 Thesis/article.tex
erichsen

\begin{document}
\maketitle
\iffalse
my notes
\fi
%\begin{acronym}
%	\newacronym{nemo}{amat}{dolorem}
	\newacronym{zrpro}{Zr(PrO)$_4$}{zirconium(IV)propoxide}
	\newacronym{acac}{Hacac}{acetylacetone}
	\newacronym{acoh}{AcOH}{acetic acid}
	\newacronym{buoh}{BuOH}{1-buthanol}
	\newacronym{ipo}{IPO}{2-Propanol}
	\newacronym{ito}{ITO}{indium doped tin oxide}
	\newacronym{fto}{FTO}{fluorine doped tin oxide}
	\newacronym{n2}{N$_2$}{nitrogen}
	\newacronym{water}{H$_2$O}{deionized water}
	\newacronym{sds}{SDS}{sodium dodecyl sulfate}
	\newacronym{hcl}{HCl}{hydrochloric acid}
	\newacronym{h2so4}{H$_2$SO$_4$}{sulfuric acid}
	\newacronym{naoh}{NaOH}{sodium hydroxide}
	\newacronym{zro}{ZrO$_2$}{zirconium dioxide}
	\newacronym{1f}{1F}{one-fold concentrated solution}
	\newacronym{2f}{2F}{two-fold concentrated solution}
	\newacronym{3f}{3F}{three-fold concentrated solution}
	\newacronym{4f}{4F}{four-fold concentrated solution}
	\newacronym{5f}{5F}{five-fold concentrated solution}
%\end{acronym}

%\clearpage
\printglossaries
%\clearpage
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preface}
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Aims and Objectives}
was hab ich gemacht, warum? 
Defensio: Argumente in der Arbeit noch mal sichten, Feedback von Betreuungsperson im Kopf haben - da könnten Fragen kommen, 
sich selbst aufnehmen

Präsentieren: Visualisierungen sinnvoll? 
Antworten überlegen/Argumente überlegen
Limitation, Rahmen der Arbeit
Begründung für die eigene Vorgehensweise
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL
\section{Experimental}
\label{sec:exp}
In this section the used chemicals and substrates, experimental procedures and any used equipment are described. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (2.5~cm~x~7.5~cm) \td{from where}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from where}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from where}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) \td{provided by Sunplugged~(\url{http://sunplugged.at/)}}.
The glass slides and \gls{fto} were cut with a \td{diamond scratcher} and broken with a \td{glass breaker} into pieces of dimensions 2.5~cm~x~2.5~cm.
The steel foil was cut with a foil cutter\me{, a cutter knife repeatedly, a paper cutter or a scissors (ordered by increasing curvature of resulting slides)}.
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item 15 minutes in 50 ml \gls{water} and 1 ml of Hellmanex III in a sonic bath
	\item 15 minutes in \gls{water} in a sonic bath
	\item 15 minutes in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were dry blown with dry \gls{n2} gas.

@@

Two main recipes were used and their ingredients were varied. 

@@

The procedure for the aquatic solution is as follows: 

@@

@@

The \gls{1f}

@@

The procedure for obtaining the \gls{1f} solution will be explained in detail:

@@

4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with cap) with a stirrer. 

@@

\subsection{Doctor blading}
\label{sec:DB}
The temperature of the heating plate is set to 200 $^o$C.
The temperature of the vacuum plate is set and waited until reached.
The sample is placed on the vacuum plate and tested if it can be held by the under pressure.
The velocity is set and a mini test run is performed. 
The blade is put in position. 
100-125 $\mu$l of solution is applied with an 10-1000 $\mu$l pipette and the doctor blading is started immediately. 
After evaporation of the solution, the vacuum is turned of, the 'blade pusher' put into initial position, the blade removed and excess solution removed with a wipe. 
The small metal plate is transferred to the hot heating plate and rests on there for 3-5 min. 
The process is repeated as wished.

>>>>

\begin{document}
\maketitle
\iffalse
my notes
\fi
%\begin{acronym}
%	\newacronym{nemo}{amat}{dolorem}
	\newacronym{zrpro}{Zr(PrO)$_4$}{zirconium(IV)propoxide}
	\newacronym{acac}{Hacac}{acetylacetone}
	\newacronym{acoh}{AcOH}{acetic acid}
	\newacronym{buoh}{BuOH}{1-buthanol}
	\newacronym{ipo}{IPO}{2-Propanol}
	\newacronym{ito}{ITO}{indium doped tin oxide}
	\newacronym{fto}{FTO}{fluorine doped tin oxide}
	\newacronym{n2}{N$_2$}{nitrogen}
	\newacronym{water}{H$_2$O}{deionized water}
	\newacronym{sds}{SDS}{sodium dodecyl sulfate}
	\newacronym{hcl}{HCl}{hydrochloric acid}
	\newacronym{h2so4}{H$_2$SO$_4$}{sulfuric acid}
	\newacronym{naoh}{NaOH}{sodium hydroxide}
	\newacronym{zro}{ZrO$_2$}{zirconium dioxide}
	\newacronym{1f}{1F}{one-fold concentrated solution}
	\newacronym{2f}{2F}{two-fold concentrated solution}
	\newacronym{3f}{3F}{three-fold concentrated solution}
	\newacronym{4f}{4F}{four-fold concentrated solution}
	\newacronym{5f}{5F}{five-fold concentrated solution}
	\newacronym{db}{DB}{doctor blading}
%\end{acronym}

%\clearpage
\printglossaries
%\clearpage
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preface}
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\td{describe everything what is meantioned in \ref{sec:exp}}
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Aims and Objectives}
was hab ich gemacht, warum? 
Defensio: Argumente in der Arbeit noch mal sichten, Feedback von Betreuungsperson im Kopf haben - da könnten Fragen kommen, 
sich selbst aufnehmen

Präsentieren: Visualisierungen sinnvoll? 
Antworten überlegen/Argumente überlegen
Limitation, Rahmen der Arbeit
Begründung für die eigene Vorgehensweise
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL
\section{Experimental}
\label{sec:exp}
In this section the used chemicals and substrates, experimental procedures and any used equipment are described. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (2.5~cm~x~7.5~cm) \td{from where}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from where}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from where}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) \td{provided by Sunplugged GmbH (\url{http://sunplugged.at/)}}.
The glass slides and \gls{fto} were cut\td{/scratched} with a \td{diamond scratcher/scraper} and broken with a \td{glass breaker} into pieces of dimensions 2.5~cm~x~2.5~cm.
The steel foil was cut with a foil cutter\me{, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting slides)}.
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item 15 minutes in 50 ml \gls{water} and 1 ml of Hellmanex III in a sonic bath
	\item 15 minutes in \gls{water} in a sonic bath
	\item 15 minutes in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were dry blown with dry \gls{n2} gas.

@@

Two main recipes were used and their \td{ingredients/compositions} were varied. 

@@

\me{The procedure for the aquatic solution is as follows:}

@@

\td{make recipe general}

@@

The \gls{1f} \td{(one fold (1F) solution /or/ one fold solution (1F))}

@@

The procedure for obtaining the \gls{1f} solution will be explained in detail: \td{maybe just keep it general}

@@

4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with \td{an air-tight} cap) with a stirrer. 

@@

\subsection{Doctor blading}
\label{sec:DB}
\begin{figure}
	\centering
	\includegraphics[width=.8\textwidth]{Pics/erichsen.png}
	\caption{Erichsen Coatmaster 510 
		%Doctor blading machine 
		with vacuum pump in the background and temperature regulator on the left.}
	\label{fig:eric}
\end{figure}
\td{picture of the machine, and name of the machine}
The temperature of the heating plate is set to 200 $^o$C.
The temperature of the vacuum plate is set and waited until reached.
The sample is placed on the vacuum plate and tested if it can be \td{held/retained} by the underpressure.
The velocity of the \gls{db} blade is set and a mini test run is performed. 
The blade is put in position. 
100-125 $\mu$l of solution is applied with an 10-1000 $\mu$l pipette and the doctor blading is started immediately. 
After evaporation of the solution, the vacuum is turned of, the 'blade pusher' put into initial position, the blade removed and excess solution removed with a wipe. 
The small metal plate is transferred to the hot heating plate and rests on there for 3-5 min. 
The process is repeated as wished.
